---
format: gfm
execute:
  echo: false
  message: false
  warning: false
editor_options: 
  chunk_output_type: console
---

# Smart System Education Platform

```{r setup, include=FALSE}
file_path <- fs::path_real("README.qmd")
path_components <- strsplit(as.character(file_path), "/")[[1]]
shortened_path <- fs::path_join(path_components[-(1:6)])
```

## Location: `r shortened_path`

### Description

This is the main directory.

### Directories & Files

The repository has the following directory tree.

```{r echo=FALSE}
fs::dir_tree(recurse = FALSE)
```

A short description of the directories can be found below.

| name     | description                                                                                                          | contribution |
|----------|----------------------------------------------------------------------------------------------------------------------|--------------|
| docs     | This directory hosts the files for the website                                                                       | Nick         |
| firmware | This directory hosts the firmware                                                                                    | Nick         |
| hardware | This directory hosts files and information about the hardware                                                        | Nick         |
| software | This directory includes libraries, custom libraries and example code, such as the for example the networking library | Nick         |
| overleaf | Latex Report Code                                                                                                    | Nick         |
| rstudio  | R Code                                                                                                               | Nick         |
