---
format: gfm
execute:
  echo: false
  message: false
  warning: false
editor: visual
editor_options: 
  chunk_output_type: console
---

# Smart System Education Platform

```{r setup, include=FALSE}
file_path <- fs::path_real("README.qmd")
path_components <- strsplit(file_path, "/")[[1]]
shortened_path <- fs::path_join(path_components[-c(2, 3)])
```

## Location: `r shortened_path`

### Description

This directory hosts code for the smart modules.

### Directories & Files

The repository has the following directory tree.

```{r}
fs::dir_tree(recurse = 1)
```

A short description of the directories can be found below.

| name         | description                             | contribution |
|--------------|-----------------------------------------|--------------|
| libraries    | Useful libraries for inputs and outputs | Nick         |
| networking   | Smart Module Networking library         | Nick         |
| applications | Various coding tools and applications   | Nick         |
| archive      | Old or outdated code or examples        | Nick         |

### Helpful links:

ESP-NOW <https://docs.micropython.org/en/latest/library/espnow.html>\
Networking <https://docs.micropython.org/en/latest/library/network.html>\
AP / WiFi <https://docs.micropython.org/en/latest/library/network.WLAN.html>

<https://chrisrogers.pyscriptapps.com/nick-esp-now/latest/>

[https://pyscript.com/\@chrisrogers/nick-esp-now/latest?files=README.md,sample.py](https://pyscript.com/@chrisrogers/nick-esp-now/latest?files=README.md,sample.py){.uri}

[https://pyscript.com/\@nickart/chris-nick-esp-now/latest?files=main.py,index.html,pyscript.toml,styles.css](https://pyscript.com/@nickart/chris-nick-esp-now/latest?files=main.py,index.html,pyscript.toml,styles.css){.uri}

[https://pyscript.com/\@nickart/floral-firefly/latest?files=main.py,index.html,pyscript.toml,style.css](https://pyscript.com/@nickart/floral-firefly/latest?files=main.py,index.html,pyscript.toml,style.css){.uri}

<https://github.com/micropython/webrepl>

<https://micropython.org/webrepl/?>

<https://chrisrogers.pyscriptapps.com/cbr-libraries/latest/core/andrea_terminal.py>

<https://chrisrogers.pyscriptapps.com/cbr-libraries/latest/core/restapi.py>

<https://chrisrogers.pyscriptapps.com/cbr-libraries/latest/core/file_os.py>

<https://chrisrogers.pyscriptapps.com/cbr-libraries/latest/core/file_transfer.py>

[https://cdn.jsdelivr.net/npm/micro-repl\@0.5.1/serial/+esm](https://cdn.jsdelivr.net/npm/micro-repl@0.5.1/serial/+esm)

<https://chrisrogers.pyscriptapps.com/cbr-libraries/latest/core/Tabs.py>

<https://chrisrogers.pyscriptapps.com/cbr-libraries/latest/core/andrea_terminal.py>

<https://xtermjs.org/>

[https://cdn.jsdelivr.net/npm/micro-repl\@0.5.1/serial.js](https://cdn.jsdelivr.net/npm/micro-repl@0.5.1/serial.js)
