\cleardoublepage%
\chapter{\label{chap:res}Results and Discussion}%

This is where you present your findings. As much as possible, structure your results along the lines of your research questions. Start with the simplest results first and proceed to more complex ones. Tables and Figures should be clear enough that they need little explanation: do not simply re-write the numbers as text to fill space. Rather, highlight trends, outliers, or gaps. 

\section{\label{sec:res_design}Platform and Framework Design} %reference to methods


Put in the design and architecture of the platform,

the road map,

and present the developed GitHub page, layout, website, guides and stuff and its capabilities






\section{\label{sec:res_capabilities}Smart System} %reference to methods

\subsection{\label{sec:res_website}Website}

Website and quick start Guides

present google website score

\subsection{\label{sec:res_ide}IDE and Network Management}

pyscript page, and perhaps mention the Ai idea and other stuff

\subsection{\label{sec:res_hardware}Hardware}

Module approach

Future board

etc.

\subsection{\label{sec:res_software}Software}

\subsubsection{\label{sec:res_networking}Networking}%should this be in firmware?

Also include results for experiments for range, rssi and latency.

mention playground project which made a lot of use of networking capability

Limitations of networking...

\section{\label{sec:res_validation}Validation}

\subsection{\label{sec:res_examplekit}Example Robotics Kit and Showcase}

\subsection{\label{sec:res_hackathon}Hackathon}

\subsection{\label{sec:res_honourablementions}Mention of Projects that have used the Platform for Development}

Limitations?
