%\thispagestyle{empty}%
\chapter*{Acknowledgements}%
\markboth{\MakeUppercase{Acknowledgements}}{\MakeUppercase{Acknowledgements}}%
\phantomsection%

The completion of this thesis would not have been possible without the support, guidance and encouragement of many people to whom I am deeply grateful.\\

First and foremost, I would like to thank my parents for their unwavering support throughout this endeavour. Despite the distance from home, their encouragement and belief in me provided the strength and motivation needed to persevere.\\

I am profoundly grateful to my friends, both old and new, near and far, for their encouragement and companionship that kept me grounded throughout this journey. \\

I would like to extend my sincere gratitude to Liz for her invaluable guidance throughout my Master's degree and support in shaping this thesis. Her mentorship has been instrumental in making all of this possible. \\

In addition, I would like to especially thank Chris for his hospitality in hosting me at the Tufts Center for Engineering Education and Outreach (CEEO) and for his continued support, guidance and insights which have been instrumental in fostering my research and personal growth throughout this process. \\

I would also like to thank Milan and Jenn, who, together with Chris, constituted defence committee and provided me with valuable insights and feedback. \\

Further, I would like to express my gratitude to all the members of the CEEO, many of whom I consider dear friends. Collaborating with them has been a privilege, and their work, feedback and support have contributed to this project and greatly enriched my visit. To everyone who has been a part of this journey - thank you!