---
format: gfm
execute:
  echo: false
  message: false
  warning: false
editor: visual
editor_options: 
  chunk_output_type: console
---

# Smart System Education Platform

```{r setup, include=FALSE}
file_path <- fs::path_real("README.qmd")
path_components <- strsplit(file_path, "/")[[1]]
shortened_path <- fs::path_join(path_components[-c(2, 3)])
```

## Location: `r shortened_path`

### Description

This directory hosts the main code for the smart modules.

### Directories & Files

The repository has the following directory tree.

```{r}
fs::dir_tree(recurse = 1)
```

A short description of the directories can be found below.

| name         | description                             | contribution |
|--------------|-----------------------------------------|--------------|
| boot.py    | Smart Module Net Boot File (needs module specific main files)	 | Nick         |
| main.py      | Smart Module Main.py (manually runs module main files named after module configuration)		         | Nick         |
| am1.py    | Admin Module Main	 | Nick         |
| sl1.py    | Smart Light Main	 | Nick         |
| sm3.py    | Smart Motor Main	 | Nick         |