---
format: gfm
execute:
  echo: false
  message: false
  warning: false
editor: visual
editor_options: 
  chunk_output_type: console
---

# Smart System Education Platform

```{r setup, include=FALSE}
file_path <- fs::path_real("README.qmd")
path_components <- strsplit(file_path, "/")[[1]]
shortened_path <- fs::path_join(path_components[-c(2, 3)])
```

## Location: `r shortened_path`

### Description

This directory hosts used and useful libraries.

### Directories & Files

The repository has the following directory tree.

```{r}
fs::dir_tree(recurse = FALSE)
```

A short description of the directories can be found below.

| name           | description                               | contribution |
|----------------|-------------------------------------------|--------------|
| adxl345.py	 | Support for the built in accelerometer https://github.com/DFRobot/micropython-dflib/blob/master/ADXL345/user_lib/ADXL345.py | Milan        |
| files.py	 | Custom save to file library		     | Milan        |
| icons.py	 | Icon support for the smart motor module   | Milan        |
| sensors.py	 | Sensor support for the smart motor module | Milan        |
| servo.py	 | Servo support for the smart motor module  | Milan        |
| smartmotor.py	 | Smart motor module main program	     | Milan        |
| ssd1306.py	 | Support for the built in OLED screen https://github.com/stlehmann/micropython-ssd1306/blob/master/ssd1306.py | Milan        |
| variableLED.py | Library that powers the variable LED grid | Sophie       |
